---
title: "Analyses of Missing Data As a Function of Suicidal Events during the Study"
output: html_document
date: "2022-08-23"
---

# All analyses in this script are between-person

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Matrix)
library(dbplyr)
library(tidyverse)
library(lubridate)
library(lme4)
library(mice)
library(gghalves)
library(emmeans)
library(naniar)
library(broom.mixed)
library(lmerTest)
library(scales)
library(ggdist)
library(scipub)
library(brms)
library(GGally)
source('model_wrapper_functions.R')
beta_prior = c(prior_string("student_t(3, 0, 10)", class = "b"))
```

# Load daily data

```{r}
load('../../cleaned_data/cleaned_data_for_daily_models.rda')
load('../../cleaned_data/cleaned_baseline_data.rda')

daily = left_join(daily, self_report_baseline, by = 'ID')
daily = dplyr::filter(daily, day_num <= 200)
daily = dplyr::filter(daily, TIMEPNT==6) %>%
    mutate(no_passive = ifelse(missing_gps == 1 & missing_accel == 1 & missing_keyboard == 1, 1, 0))

load('../../cleaned_data/risk.rda')

risk_missing = risk_week_present %>%
  dplyr::filter(week_num <= 28, days ==7) %>%
  group_by(ID) %>%
  mutate(personal_time_z = scale(week_num),
         summerbreak = month %in% c(7, 8),
         site = ifelse(startsWith(ID, '1'), 'CUIMC', 'UPMC'),
         siteCUMC = site == 'CUIMC') %>%
  ungroup() %>%
  left_join(., self_report_baseline, by = 'ID')
```

# Load and Clean STB Report Data 
```{r}
stb_report = readxl::read_xlsx('../../../../../Suicidality_Report/MAPS_Suicidality_Report_2.17.23/AB_Checking_MAPS_suicidality_report.xlsx')

events = dplyr::select(stb_report, ID=ptid, event_type=event, date = start, everything()) %>%
  dplyr::filter(Origin != 'MISTAKE' | is.na(Origin)) %>%
  mutate(ID = as.character(ID),
         length_days = as.numeric(as.Date(end) - as.Date(date)),
         length_days = ifelse(is.na(length_days), 1, length_days)) %>%
  # remove events lasting more than 2 months
  dplyr::filter(!length_days > 60) %>%
  unique() %>%
  # 2 categories of events, #2 is more inclusive -- plan + ema trigger
  mutate(event_cat1 = ifelse(event_type %in% c('aborted', 'attempt', 'interrupted','ER - suicidality', 'hospitalization - suicidality'), 1, 0),
         # event cat 1 can include EMA trigger attempt if confirmed by SITBI
         event_cat1 = ifelse(event_type == 'ema trigger' & grepl('attempt', note) & `Confirmed by SITBI?`=='y' &
                               !is.na(`Confirmed by SITBI?`), 1,event_cat1),
         event_cat2 = ifelse(event_cat1==1 | event_type %in% c('plan', 'ema trigger'), 1, 0)) %>%
  # group by person-days because there might be multiple events coded in a day
  group_by(ID, date) %>%
  summarise(event_cat1 = ifelse(sum(event_cat1) >=1, 1, 0), 
            event_cat2 = ifelse(sum(event_cat2) >=1, 1, 0))


participants_events = events %>%
  group_by(ID) %>%
  summarise(event_cat1 = ifelse(sum(event_cat1)>=1, 1, 0),
            event_cat2 = ifelse(sum(event_cat2)>=1, 1, 0)) 

```
# Merge participant-level STB events with daily

```{r}
# merge events to daily dataframe
daily = left_join(daily, participants_events, by = c('ID'))

# any person-days not included in the events frame will be treated as NA. Assume no events on these days and fill with 0
daily = mutate(daily, 
               event_cat1_participant = ifelse(is.na(event_cat1), 0, event_cat1),
               event_cat2_participant = ifelse(is.na(event_cat2), 0, event_cat2))


daily_event_summary = daily %>%
  group_by(ID, event_cat1_participant, event_cat2_participant) %>%
  count()


sum(daily_event_summary$event_cat1_participant)
sum(daily_event_summary$event_cat2_participant)

```

# Model formulas
```{r}
sociodemographic_predictors = sociodemographic_predictors[! sociodemographic_predictors %in% 
                                                                 c('White', 'interview_date_numeric')]

event_cat1_formula = as.formula(paste('value ~ event_cat1_participant + (1|ID)'))
event_cat2_formula = as.formula(paste('value ~ event_cat2_participant + (1|ID)'))

event_cat1_formula_nopassive = as.formula(paste('value ~ event_cat1_participant + no_passive + (1|ID)'))

event_cat1_formula_sociodem = as.formula(paste('value ~ event_cat1_participant + ', 
                                     paste(sociodemographic_predictors, collapse = '+'), ' + (1|ID)'))
event_cat2_formula_sociodem = as.formula(paste('value ~ event_cat2_participant + ', 
                                     paste(sociodemographic_predictors, collapse = '+'), ' + (1|ID)'))

event_cat1_formula_within = as.formula(paste('value ~ event_cat1_participant + weekend + personal_time_z + summerbreak + (1|ID)'))
event_cat2_formula_within = as.formula(paste('value ~ event_cat2_participant + weekend + personal_time_z + summerbreak + (1|ID)'))


event_cat1_formula_within_risk = as.formula(paste('value ~ event_cat1_participant + personal_time_z + summerbreak + (1|ID)'))
event_cat2_formula_within_risk = as.formula(paste('value ~ event_cat2_participant + personal_time_z + summerbreak + (1|ID)'))
```


# Daily models based on suicide events
```{r}
iter = 4000
event_cat1_daily_models = daily %>%
  pivot_longer(contains('missing')) %>%
  group_by(name) %>%
  nest() %>%
  mutate(model = purrr::map(data, ~brms::brm(data = ., formula = event_cat1_formula, 
                                               family = bernoulli(link = 'logit'), 
                                             cores = 4, chains = 4, iter = iter, seed = 11291993,
                                             prior = beta_prior)),
           coef = purrr::map(model, ~fixef(., probs =c(0.025, 0.975)) %>%
                               exp(.) %>%
                               as.data.frame(.) %>%
                               rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.))),
         modeltype = 'No Covariates')

event_cat1_daily_models_sociodem = daily %>%
  pivot_longer(contains('missing')) %>%
  group_by(name) %>%
  nest() %>%
  mutate(model = purrr::map(data, ~brms::brm(data = ., formula = event_cat1_formula_sociodem, 
                                               family = bernoulli(link = 'logit'), 
                                             cores = 4, chains = 4, iter = iter, seed = 11291993,
                                             prior = beta_prior)),
           coef = purrr::map(model, ~fixef(., probs =c(0.025, 0.975)) %>%
                               exp(.) %>%
                               as.data.frame(.) %>%
          rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.))),
         modeltype = 'Including Sociodemographic Covariates')
```

```{r}
event_cat1_daily_models_within = daily %>%
  pivot_longer(contains('missing')) %>%
  group_by(name) %>%
  nest() %>%
  mutate(model = purrr::map(data, ~brms::brm(data = ., formula = event_cat1_formula_within, 
                                               family = bernoulli(link = 'logit'), 
                                             cores = 4, chains = 4, iter = iter, seed = 11291993,
                                             prior = beta_prior)),
           coef = purrr::map(model, ~fixef(., probs =c(0.025, 0.975)) %>%
                               exp(.) %>%
                               as.data.frame(.) %>%
                               rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.))),
         modeltype = 'Including Time-Varying Covariates')

event_cat1_daily_models_no_passive = daily %>%
  pivot_longer(contains('missing_daily')) %>%
  group_by(name) %>%
  nest() %>%
  mutate(model = purrr::map(data, ~brms::brm(data = ., formula = event_cat1_formula_nopassive, 
                                               family = bernoulli(link = 'logit'), 
                                             cores = 4, chains = 4, iter = iter, seed = 11291993,
                                             prior = beta_prior)),
           coef = purrr::map(model, ~fixef(., probs =c(0.025, 0.975)) %>%
                               exp(.) %>%
                               as.data.frame(.) %>%
                               rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.))),
         modeltype = 'Adjusting for Days With No Smartphone Sensor Data')



event_cat1_all_models = rbind(event_cat1_daily_models, event_cat1_daily_models_sociodem, event_cat1_daily_models_within, event_cat1_daily_models_no_passive)
```

# Clean data for weekly SI models

```{r}
# merge events to daily dataframe
risk_missing = left_join(risk_missing, participants_events, by = c('ID'))

# any person-days not included in the events frame will be treated as NA. Assume no events on these days and fill with 0
risk_missing = mutate(risk_missing, 
               event_cat1_participant = ifelse(is.na(event_cat1), 0, event_cat1),
               event_cat2_participant = ifelse(is.na(event_cat2), 0, event_cat2))

risk_missing = mutate(risk_missing, value = risk_missing)

risk_missing = left_join(risk_missing, dplyr::select(daily, no_passive, ID, week=date), by = c('ID', 'week'))

```

# Weekly SI models

```{r}
risk_missing_cat1_model = brms::brm(data = risk_missing, formula = event_cat1_formula, family = bernoulli(link = 'logit'), 
                                      cores = 4, chains = 4, iter = iter, seed = 11291993, prior = beta_prior)
risk_missing_cat1_model_sociodem = brms::brm(data = risk_missing, formula = event_cat1_formula_sociodem, family = bernoulli(link = 'logit'), 
                                      cores = 4, chains = 4, iter = iter, seed = 11291993, prior = beta_prior)
risk_missing_cat1_model_within = brms::brm(data = risk_missing, formula = event_cat1_formula_within_risk, family = bernoulli(link = 'logit'), 
                                      cores = 4, chains = 4, iter = iter, seed = 11291993, prior = beta_prior)
risk_missing_cat1_model_nopassive = brms::brm(data = risk_missing, formula = event_cat1_formula_nopassive, family = bernoulli(link = 'logit'), 
                                      cores = 4, chains = 4, iter = iter, seed = 11291993, prior = beta_prior)
```

# Save model outputs 

```{r}
save(event_cat1_all_models, 
     risk_missing_cat1_model, 
     risk_missing_cat1_model_sociodem,
     risk_missing_cat1_model_within,
     risk_missing_cat1_model_nopassive,
     file = 'model_outputs/stb_during_study_models.rda')
```


# Pull OR from weekly models
```{r}
risk_missing_cat1_or = fixef(risk_missing_cat1_model, probs =c(0.025, 0.975)) %>% exp() %>% as.data.frame(.) %>%
                               rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.),
                                                modeltype = 'No Covariates', name = 'Weekly SI Survey')

risk_missing_cat1_or_sociodem = fixef(risk_missing_cat1_model_sociodem, probs =c(0.025, 0.975)) %>% exp() %>% as.data.frame(.) %>%
                               rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.),
                                                modeltype = 'Including Sociodemographic Covariates', name = 'Weekly SI Survey')

risk_missing_cat1_or_within = fixef(risk_missing_cat1_model_within, probs =c(0.025, 0.975)) %>% exp() %>% as.data.frame(.) %>%
                               rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.),
                                                modeltype = 'Including Time-Varying Covariates', name = 'Weekly SI Survey')

risk_missing_cat1_or_nopassive = fixef(risk_missing_cat1_model_nopassive, probs =c(0.025, 0.975)) %>% exp() %>% as.data.frame(.) %>%
                               rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.),
                                                modeltype = 'Adjusting for Days With No Smartphone Sensor Data', name = 'Weekly SI Survey')

risk_missing_cat1_or_all = rbind(risk_missing_cat1_or, risk_missing_cat1_or_within, risk_missing_cat1_or_sociodem, risk_missing_cat1_or_nopassive)

```

# Clean up OR and make plot

```{r}
event_cat1_daily_or = event_cat1_all_models %>%
    unnest(coef) %>%
    dplyr::select(-model, -data)


event_cat1_or = rbind(event_cat1_daily_or, risk_missing_cat1_or_all) %>%
  mutate(name = dplyr::recode(name,
  'missing_accel'='Accelerometer',
                              'missing_gps'='GPS',
                              'missing_keyboard'='Keyboard Input',
                              'missing_daily'='Daily Mood Survey'))

stb_missing_data_plot = event_cat1_or %>%
  dplyr::filter(term == 'event_cat1_participant') %>%
  ggplot(data = ., aes(x = name, y = estimate, color = modeltype)) +
  geom_hline(yintercept = 1, lty = 2) +
  geom_point(position = position_dodge(0.2)) + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0, position = position_dodge(0.2)) +
  coord_flip() +
  scale_y_log10() +
  labs(y = 'Odds Ratio for Probability of Missing Data\nParticipants with 1+ Suicidal Events > Participants With 0 Suicidal Events During Study Period',
       color = 'Model Specification',
       x = 'Missing Data Modality',
       subtitle = 'No Significant Differences in Missing Data For Participants With vs. Without Suicidal Events During Study Period') +
  theme_bw() +
  scale_color_viridis_d()


ggsave(stb_missing_data_plot, filename = '../../figures/supplement/stb_during_study_period_or.png', width = 9, height = 5)
```

```{r}
summary(risk_missing_cat1_model_sociodem)
```

# Summary Boxplot
```{r}
by_event = daily %>%
  group_by(ID, event_cat1_participant) %>%
  summarise(prop_missing_daily = sum(missing_daily)/n(),
            prop_missing_gps = sum(missing_gps)/n(),
            prop_missing_keyboard = sum(missing_keyboard)/n(),
            prop_missing_accel = sum(missing_accel)/n()) %>%
  mutate(event_cat1_label = ifelse(event_cat1_participant==1, '1+ Events', 'No Events'))

by_event_risk = risk_missing %>%
  group_by(ID, event_cat1_participant) %>%
  summarise(prop_missing_risk = sum(risk_missing)/n())%>%
  mutate(event_cat1_label = ifelse(event_cat1_participant==1, '1+ Events', 'No Events'))
 

by_event_all = left_join(by_event, by_event_risk, by = c('ID', 'event_cat1_participant', 'event_cat1_label'))
```

# Plots of raw data

```{r}
pal2 = c(rgb(0,0,0), rgb(230/255, 159/255,0), rgb(86/255,180/255,233/255), rgb(204/255, 121/255, 167/255), rgb(0, 158/255, 115/255), rgb(0, 114/255, 178/255))

suicidal_behavior_missingngess = by_event_all %>%
  pivot_longer(contains('prop')) %>%
  dplyr::mutate(name = dplyr::recode(name, 'prop_missing_daily'='Daily Mood Survey', 'prop_missing_gps'='GPS', 'prop_missing_risk'='Weekly SI Survey',
                                           'prop_missing_keyboard'='Keyboard Input', 'prop_missing_accel'='Accelerometer')) %>%
  ggplot(aes(x = event_cat1_label, y = value*100, fill = name)) +
  gghalves::geom_half_violin(position = position_nudge(-0.15), alpha = 0.4) + 
  geom_boxplot(width = 0.05, position = position_nudge(-0.1), outlier.shape = NA, alpha = 0.4) +
  geom_jitter(width = 0.05, alpha = 0.3) +
  theme_bw() +
  labs(y = '% Observations Mising', x = 'Participants With 1+ Suicidal Events Versus No Suicidal Events During the Study Period') +
  theme(legend.position = 'none') +
  facet_grid(~name) +
  scale_fill_manual(values= c(
      "Accelerometer" = pal2[1], 
      "Daily Mood Survey" = pal2[2], 
      "GPS" = pal2[3], 
      "Keyboard Input" = pal2[4], 
      "Weekly SI Survey" = pal2[5]
    ),
    limits= c(
      "Keyboard Input", 
      "GPS", 
      "Accelerometer",
      "Weekly SI Survey",
      "Daily Mood Survey"
    ))




ggsave(suicidal_behavior_missingngess, file = '../../figures/supplement/boxplot_stb_during_study_vis.png', height = 3, width = 9)
```

# Same analysis using `lm()`

```{r}
event_lm = by_event_all %>%
  pivot_longer(contains('prop')) %>%
  group_by(name) %>%
  nest() %>%
  mutate(model = purrr::map(data, ~lm(data =., value ~ event_cat1_label)),
         coef = purrr::map(model, ~broom::tidy(.))) %>%
  unnest(coef)


event_lm %>%
  dplyr::filter()
```