---
title: "Temporal Factor Associations With Missingness"
output: html_document
date: "2022-08-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Matrix)
library(dbplyr)
library(tidyverse)
library(lubridate)
library(lme4)
library(mice)
library(gghalves)
library(emmeans)
library(naniar)
library(broom.mixed)
library(lmerTest)
library(scales)
library(brms)
library(ggrepel)
theme_set(theme_bw())
source('model_wrapper_functions.R')
```

# Define Color Palettes

```{r}
# Palette from http://mkweb.bcgsc.ca/colorblind/palettes/8.color.blindness.palette.txt
pal = c('#000000','#d55e00', '#3DB7E9', '#F748A5', '#359B73','#2271B2', '#e69f00', '#f0e442')
pal2 = c(rgb(0,0,0), rgb(230/255, 159/255,0), rgb(86/255,180/255,233/255), rgb(204/255, 121/255, 167/255), rgb(0, 158/255, 115/255), rgb(0, 114/255, 178/255))

load('../../cleaned_data/cleaned_data_for_daily_models.rda')
```


```{r}
load('../../cleaned_data/risk.rda')
daily = dplyr::filter(daily, TIMEPNT==6, day_num < 200)
```

# 1. Models for OR

## Time models for daily & passive 
```{r}
comparisons = 3
conf_level_corrected = 1-(0.05/comparisons)

beta_prior = c(prior_string("student_t(3, 0, 10)", class = "b"))

daily_long = daily %>%
  group_by(ID) %>%
  mutate(day_num_center = scale(day_num, center = TRUE, scale = FALSE)) %>%
  ungroup() %>%
  mutate(week_num_center = day_num_center/7,
         month_num_center = day_num_center/30.4) %>%
  pivot_longer(contains('missing')) 
```

## Run models
```{r}
time_models_daily_basis = daily_long %>% group_by(name) %>%
  nest() %>%
  mutate(time_model =  purrr::map(data, ~brms::brm(data = ., value ~ month_num_center + summerbreak + weekend + (month_num_center + summerbreak + weekend|ID),
                                                         family = bernoulli(link = 'logit'), 
                                                   cores = 4, chains = 4, iter = 4000, seed = 11291993,
                                                   prior = beta_prior)))
```
 

## Time model for weekly SI 
```{r}
risk_week_present = mutate(risk_week_present, 
                           week_num_center = scale(week_num, center = TRUE, scale = FALSE),
                           month_num_center = week_num_center/4.3,
                           summerbreak=factor(ifelse(month %in% c(7,8), 1, 0))) %>%
    dplyr::filter(week_num <= 27, week_num > 1, TIMEPNT==6) 


time_model_week_risk = brms::brm(data = risk_week_present, risk_missing ~ month_num_center + summerbreak + (month_num_center + summerbreak |ID),
                                                         family = bernoulli(link = 'logit'), 
                                                   cores = 4, chains = 4, iter = 4000, seed = 11291993,
                                                   prior = beta_prior)

save(time_models_daily_basis, time_model_week_risk, file = 'model_outputs/design_features_predict_missingness.rda')
```


## Calculate Or


## Risk OR
```{r}
load('model_outputs/design_features_predict_missingness.rda')
time_or_week_risk_uncorrected = time_model_week_risk %>% fixef(., probs =c(0.025, 0.975)) %>%
                                         exp() %>%
                                         as.data.frame(.) %>%
                                         rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.)) %>%
  mutate(name = 'Weekly SI Survey', corrected = 'or_uncorrected')

time_or_week_risk_corrected = time_model_week_risk %>% fixef(., probs =c((1-conf_level_corrected)/2, 
                                                                 1-(1-conf_level_corrected)/2)) %>%
                                         exp() %>%
                                         as.data.frame(.) %>%
                                         rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.)) %>%
  mutate(name = 'Weekly SI Survey', corrected = 'or_corrected')


time_or_week_risk = rbind(time_or_week_risk_corrected, time_or_week_risk_uncorrected)

```

### OR for daily time models
```{r}
time_or_daily_basis_brm = time_models_daily_basis %>%
  mutate(or_corrected = purrr::map(time_model, ~fixef(., probs =c((1-conf_level_corrected)/2, 
                                                                 1-(1-conf_level_corrected)/2)) %>%
                                         exp() %>%
                                         as.data.frame(.) %>%
                                         rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.))),
         or_uncorrected = purrr::map(time_model, ~fixef(., probs =c(0.025, 0.975)) %>%
                                         exp() %>%
                                         as.data.frame(.) %>%
                                         rename_cols(., colnames = c('estimate', 'Est.Error', 'conf.low', 'conf.high')) %>%
                                         mutate(., term = row.names(.)))) %>%
  pivot_longer(c(or_corrected, or_uncorrected),
               names_to = 'corrected') %>%
  unnest(value) %>%
  dplyr::select(-time_model, -data)
```

## Combine outputs & plot

```{r}
time_or_daily_basis = rbind(time_or_daily_basis_brm, time_or_week_risk)


time_or_daily_basis =  time_or_daily_basis %>%
  mutate(term = dplyr::recode(term,
                              'weekend'='Weekend > Week Days',
                              'summerbreak1'='Summer Break > School Year',
                              'month_num_center'='+1 Month Since Baseline'),
         name = dplyr::recode(name,
                              'missing_accel'='Accelerometer',
                              'missing_gps'='GPS',
                              'missing_keyboard'='Keyboard Input',
                              'missing_daily'='Daily Mood Survey'))

or_plot = time_or_daily_basis %>%
  dplyr::filter(corrected == 'or_corrected') %>%
  dplyr::filter(! term %in% c('Intercept', 'sd__(Intercept)')) %>%
  ggplot(data = ., aes(x = term, y = estimate, color=name)) +
  geom_point(position = position_dodge(0.2)) + 
  geom_errorbar(data = dplyr::filter(time_or_daily_basis,
                                     corrected == 'or_uncorrected',
                                     !term %in% c('Intercept', 'sd__(Intercept)')),
                                     aes(ymin = conf.low, ymax = conf.high), width = 0, position = position_dodge(0.2),
                lwd = 1) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0, position = position_dodge(0.2)) +
  geom_hline(yintercept = 1, lty = 2) +
  coord_flip() +
  scale_y_log10() +
  labs(y = 'Association with missingness\nAdjusted Odds Ratio',
       x = NULL, color = NULL) +
  scale_color_manual(values = pal2) +
  theme(legend.position = 'none')
```

```{r}
time_or_table = time_or_daily_basis %>%
  dplyr::filter(term != 'Intercept') %>%
  dplyr::select(-Est.Error) %>%
  pivot_wider(id_cols = c('name', 'estimate', 'term'), values_from = c('conf.low', 'conf.high'), 
              names_from = corrected) %>%
   mutate(`95% CI`=paste0('[', format(round(conf.low_or_uncorrected, digits = 3), nsmall=3), ', ', format(round(conf.high_or_uncorrected, digits = 3), nsmall=3), ']'),
           `98.33% CI`=paste0('[', format(round(conf.low_or_corrected, digits = 3), nsmall=3), ', ', format(round(conf.high_or_corrected, digits = 3), nsmall=3), ']'),
           Significance = case_when(
              conf.low_or_corrected > 1 & conf.high_or_corrected > 1 ~ '#',
              conf.low_or_corrected < 1 & conf.high_or_corrected < 1 ~ '#',
              conf.low_or_uncorrected < 1 & conf.high_or_uncorrected < 1 ~ '+',
              conf.low_or_uncorrected > 1 & conf.high_or_uncorrected > 1 ~ '+')) %>%
  dplyr::select('Contrast'=term, 'Missing Data Modality'=name, `Adjusted Odds Ratio`=estimate, 
                `95% CI`, `98.33% CI`, Significance) %>%
  dplyr::arrange(Contrast, `Missing Data Modality`) %>%
  mutate(`Adjusted Odds Ratio` = format(round(`Adjusted Odds Ratio`, digits = 3), nsmall=3))

time_or_table[is.na(time_or_table)] = ''

write.csv(time_or_table, row.names = FALSE, file = '../../tables/supplement/design_features_or_table.csv')
```


# 2. Plot raw proportions of missing data over time

First calculate sliding window proportions of data over time (over week windows)
```{r}
# for calculating weekly rolling averages of missingness
rolling_proportion_missing = function(df,day_num_select, days_back, variable){
  df_filtered = dplyr::filter(df, 
                              day_num <= day_num_select, 
                              day_num > day_num_select - days_back)
  
  missing_subset <- df_filtered[, paste0(variable)]
  
  denominator = nrow(df_filtered)
  numerator = sum(missing_subset)
  
  proportion_missing = numerator/denominator
  return(proportion_missing)
}



rolling_df = data.frame(day_num = 1:180, missing_daily = rep(NA, 180),
                        missing_keyboard = rep(NA, 180),
                        missing_accel = rep(NA, 180),
                        missing_gps = rep(NA, 180))

for (i in 1:nrow(rolling_df)){
  rolling_df$missing_daily[i] = rolling_proportion_missing(df =daily, day_num_select = i, days_back = 7, variable = 'missing_daily')
  rolling_df$missing_keyboard[i] = rolling_proportion_missing(df =daily, day_num_select = i, days_back = 7, variable = 'missing_keyboard')
  rolling_df$missing_accel[i] = rolling_proportion_missing(df =daily, day_num_select = i, days_back = 7, variable = 'missing_accel')
  rolling_df$missing_gps[i] = rolling_proportion_missing(df =daily, day_num_select = i, days_back = 7, variable = 'missing_gps')
}

# # of participants
n_p = length(unique(daily$ID))

daily_day_num_proportions = rolling_df %>%
  pivot_longer(contains('missing')) %>%
  group_by(day_num, name) %>% 
  summarise(p = value,
            se = sqrt(p*(1-p)/n_p),
            lwr = p - 2*se, 
            upr = p + 2*se) %>%
  mutate(name = dplyr::recode(name, 'missing_daily'='Daily Mood Survey',
                              'missing_gps'='GPS',
                              'missing_keyboard'='Keyboard Input',
                              'missing_accel'='Accelerometer'), 
         week_num = day_num / 7) %>%
  dplyr::filter(!(day_num <=7  & name == 'Accelerometer'),
                day_num < 180)

```

Plot rolling window proportions of missing data 
```{r}
risk_week_num_proportions = risk_week_present %>%
  dplyr::select(ID, week_num, risk_missing) %>%
  group_by(week_num) %>% 
  summarise(p = sum(risk_missing)/n(),
            se = sqrt(p*(1-p)/n()),
            lwr = p - 2*se, 
            upr = p + 2*se) %>%
  mutate(name = 'Weekly SI Survey', 
         week_num = week_num - 1,
         day_num = week_num*7) %>%
  dplyr::filter(week_num <= 25)

daily_day_num_proportions = rbind(daily_day_num_proportions, risk_week_num_proportions)


time_starts = dplyr::filter(daily_day_num_proportions, week_num ==1 | (week_num == 2 & name == 'Accelerometer')) %>%
  group_by(name) %>%
  summarise(p = mean(p), week_num = 0)

time_ends = dplyr::filter(daily_day_num_proportions, week_num ==24) %>%
  group_by(name) %>%
  summarise(p = mean(p), week_num =25)

daily_day_num_proportions = dplyr::filter(daily_day_num_proportions, !(name == 'Weekly SI Survey' & week_num == 0))

timeplt = ggplot(daily_day_num_proportions, aes(x = week_num, y = p)) +
  geom_hline(yintercept = 0.5, lty = 2) +
  geom_line(aes(color = name), lwd = 1) +
  labs(y = 'P(Missing)', x = "Weeks since baseline (person-weeks)\n", color= NULL) +
  scale_x_continuous(breaks = c(0, 5, 10, 15, 20, 25)) +
  theme(legend.position = 'right') +
  ggrepel::geom_label_repel(
    aes(label = format(round(p,2), nsmall=2), color = name), data = time_starts,
    fontface ="plain",  size = 3, direction = 'both', point.padding = 1, show.legend =FALSE) +
  ggrepel::geom_label_repel(
    aes(label = format(round(p,2), nsmall=2), color = name), data = time_ends,
    fontface ="plain",  size = 3, direction = 'both', show.legend =FALSE) +
  scale_color_manual(values = pal2)
```


## Daily Mood Month & Weekday Models
```{r}
daily = mutate(daily, weds = dayofweek=='Wednesday')

# exclude weekends here to compare wednesday to other weekdays
m_weds_daily = brms::brm(data = dplyr::filter(daily, weekend == '0'), missing_daily ~  summerbreak + weds + personal_time_z + (weds |ID), 
                         family = bernoulli(link = 'logit'), cores = 4, chains = 4, iter = 4000, seed = 11291993, prior = beta_prior)
```

Daily model summaries/output

```{r}
m_weds_daily %>% emmeans::emmeans(specs = 'weds', type = 'response') %>%
  pairs(reverse=TRUE) %>%
  confint()

m_week_month = brms::brm(data = daily, missing_daily ~ dayofweek + factor(month) + personal_time_z + (1 |ID), 
                           family = bernoulli(link = 'logit'), cores = 4, chains = 4, iter = 4000, seed = 11291993, prior = beta_prior)

m_week_month_keyboard = brms::brm(data = daily, missing_keyboard ~ dayofweek + factor(month) + personal_time_z + (1 |ID), 
                           family = bernoulli(link = 'logit'), cores = 4, chains = 4, iter = 4000, seed = 11291993, prior = beta_prior)

m_week_month_accel = brms::brm(data = daily, missing_accel ~ dayofweek + factor(month) + personal_time_z + (1 |ID), 
                           family = bernoulli(link = 'logit'), cores = 4, chains = 4, iter = 4000, seed = 11291993, prior = beta_prior)

```


```{r}
save(m_weds_daily, m_week_month, m_week_month_keyboard, m_week_month_accel, file = 'model_outputs/day_of_week_month_models.rda')
```

# Plots as a function of day of week / month of year

```{r}
month_daily = emmeans::emmeans(m_week_month, specs = 'month', type = 'response',
                               at = list(personal_time_z = -1, dayofweek = 'Tuesday')) %>%
  data.frame(type = 'Daily Mood')

month_keyboard = emmeans::emmeans(m_week_month_keyboard, specs = 'month', type = 'response',
                                  at = list(personal_time_z = -1, dayofweek = 'Tuesday')) %>%
  data.frame(type = 'Keyboard Input')

month_accel= emmeans::emmeans(m_week_month_accel, specs = 'month', type = 'response',
                                  at = list(personal_time_z = -1, dayofweek = 'Tuesday')) %>%
  data.frame(type = 'Accelerometer')

week_daily = emmeans::emmeans(m_week_month, specs = 'dayofweek', type = 'response') %>%
  data.frame() %>%
  mutate(type = 'Daily Mood')

week_keyboard = emmeans::emmeans(m_week_month_keyboard, specs = 'dayofweek', type = 'response') %>%
  data.frame() %>%
  mutate(type = 'Daily Mood')
```


```{r}
weekplt = week_daily %>%
  dplyr::filter(type == 'Daily Mood') %>%
  ggplot(data = ., aes(x = dayofweek, y = response)) +
  geom_point(color = pal2[2], size = 3) +  
  geom_vline(xintercept = 'Wednesday', lty = 2, color = 'red', alpha = 0.5) +
  geom_hline(yintercept = 0.5, lty = 2) +
  geom_errorbar(aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, color = pal2[2], lwd = 1) +
  scale_x_discrete(limits = c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday', 'Sunday')) +
  labs(x = 'Day of Week', y  = 'P(Missing Daily Mood)', color = NULL) +
  annotate(geom = 'label', 
            label = 'Suicide Ideation Prompt\nDelivered 9am Weds',
            color = 'black',
            x = 'Wednesday', y = .65)

 monthplt = month_daily %>%
  rbind(., month_keyboard, month_accel) %>%
  ggplot(data = ., aes(x = month, y = response)) +
  geom_point(aes(color = type), position = position_dodge(0.3), size =3) +
  geom_hline(yintercept = 0.5, lty = 2) + 
  geom_errorbar(aes(ymin = lower.HPD, ymax = upper.HPD, color = type), width = 0, position = position_dodge(0.3)) +
  scale_x_discrete(limits = c('Jan', 'Feb', 'Mar', 'April', 'May', 'June', 'July', 'August', 'Sept','Oct', 'Nov', 'Dec')) +
  labs(x = 'Month', y  = 'P(Missing)', color = NULL)  +
  scale_color_manual(values = pal2[c(1,2,4)]) +
  theme(legend.position = 'none') +
  annotate(geom = 'label', 
            label = 'Accelerometer',
            color = pal2[1],
            x = 'Mar', y = .65) +
  annotate(geom = 'label', 
            label = 'Daily Mood Survey',
            color = pal2[2],
            x = 'Mar', y = .7) +
  annotate(geom = 'label', 
            label = 'Keyboard Input',
            color = pal2[4],
            x = 'Mar', y = .75)

```

# 4. Make plot grids

```{r}
top_row =  cowplot::plot_grid(timeplt, or_plot, labels = c('A', 'B'), rel_widths = c(1.6, 1))
bottom_row = cowplot::plot_grid(weekplt, monthplt, labels = c('C', 'D'))

design_grid = cowplot::plot_grid(top_row, bottom_row, nrow = 2)
cowplot::save_plot(design_grid, filename = '../../figures/fig3.1_design_features_daily_missingness.png', base_width = 10, base_height = 7)
```

