---
title: "Model Between-Participant Baseline Predictors of Missing Data: Supplemental Analysis Accounting for Days with No Passive Data"
output: html_document
date: "2022-08-23"
---


# Add a covariate of a binary indicator for days with no passive data collected, so that we can look at predictors of missing survey data above and beyond EARS being deactivated

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Matrix)
library(dbplyr)
library(tidyverse)
library(lubridate)
library(lme4)
library(mice)
library(gghalves)
library(emmeans)
library(naniar)
library(broom.mixed)
library(lmerTest)
library(scales)
library(brms)
#library(ggfortify)
theme_set(theme_bw())
source('model_wrapper_functions.R')
options(buildtools.check = function(action) TRUE)
```

# Data setup

```{r}
load('../../cleaned_data/cleaned_data_for_daily_models.rda')
load('../../cleaned_data/cleaned_baseline_data.rda')
```

```{r}
m = length(clinical_predictors)
corrected_conf_level = 1- (0.05/m)
```

```{r}
daily = left_join(daily, self_report_baseline, by = 'ID')
daily = dplyr::filter(daily, day_num <= 200)
daily = dplyr::filter(daily, TIMEPNT==6)
```


## Weekly risk data
```{r}
load('../../cleaned_data/risk.rda')


risk_missing = risk_week_present %>%
  dplyr::filter(week_num <= 28, days ==7) %>%
  group_by(ID) %>%
  mutate(personal_time_z = scale(week_num),
         summerbreak = month %in% c(7, 8),
         site = ifelse(startsWith(ID, '1'), 'CUIMC', 'UPMC'),
         siteCUMC = site == 'CUIMC') %>%
  ungroup() %>%
  left_join(., self_report_baseline, by = 'ID') 

risk_missing = dplyr::filter(risk_missing, TIMEPNT==6)
```

## Create binary indicator for whether there is any passive data observed
```{r}
daily = daily %>%
  mutate(no_passive = ifelse(missing_gps == 1 & missing_accel == 1 & missing_keyboard == 1, 1, 0))

risk_missing = left_join(risk_missing, dplyr::select(daily, no_passive, ID, week=date), by = c('ID', 'week'))
```



```{r}
sociodemographic_predictors = sociodemographic_predictors[!grepl('interview_date_numeric', sociodemographic_predictors)]
```

# Supplemental Analysis Adding a 1-day Lag Missingness Predictor (to account for autocorrelation of missingness)

```{r}
m_formula_template_daily_w_nopassive = as.formula(paste('missing_daily ~ no_passive +
                                                 scaled_predictor + personal_time_z + weekend + summerbreak +', 
                                            paste(sociodemographic_predictors, collapse = '+'), ' + (1 |ID)'))

m_formula_template_risk_w_nopassive = as.formula(paste('risk_missing ~ no_passive + scaled_predictor + 
                                                personal_time_z + summerbreak +', 
                                           paste(sociodemographic_predictors, collapse = '+'), ' + (1 |ID)'))
```

## Sociodemographic models
```{r}
m_sociodemographic_daily_w_nopassive = as.formula(paste('missing_daily ~ no_passive + personal_time_z + weekend + summerbreak +', 
                                            paste(sociodemographic_predictors, collapse = '+'), ' + (1 |ID)'))

m_sociodemographic_risk_w_nopassive = as.formula(paste('risk_missing ~ no_passive + personal_time_z + summerbreak +', 
                                           paste(sociodemographic_predictors, collapse = '+'), ' + (1 |ID)'))
```


# Run models & get ORs for each outcome

```{r risk_models}
risk_outputs = or_pipeline(df = risk_missing, 
                      model_formula_template = m_formula_template_risk_w_nopassive,
                      clinical_predictors = clinical_predictors,
                      conf_level_corrected = corrected_conf_level,
                      bayes=TRUE)

# Save and clear unused memory
risk_outputs = risk_outputs[names(risk_outputs) != 'models_df']
save(risk_outputs, file = 'model_outputs/baseline_predictors_missingness_brm_risk_w_nopassive.rda')
gc()
```

```{r daily_models}
daily_outputs = or_pipeline(df = daily, 
                      model_formula_template = m_formula_template_daily_w_nopassive,
                      clinical_predictors = clinical_predictors,
                      conf_level_corrected = corrected_conf_level,
                      bayes=TRUE)

# Save and clear unused memory
daily_outputs = daily_outputs[names(daily_outputs) != 'models_df']
save(daily_outputs, file = 'model_outputs/baseline_predictors_missingness_brm_daily_w_nopassive.rda')
gc()
```



```{r}
load('model_outputs/baseline_predictors_missingness_brm_daily_w_nopassive.rda')
load('model_outputs/baseline_predictors_missingness_brm_risk_w_nopassive.rda')

combined_or_bayes = rbind(risk_outputs$or_df %>% mutate(type = 'Weekly SI Survey'),
                    daily_outputs$or_df %>% mutate(type = 'Daily Mood Survey'))

clinical_or_mlm_bayes = baseline_predictors_missingness_or_plot(combined_or_bayes, m = m, bayes = TRUE)
```



# Sociodemographic models 
```{r}
# Models
daily_sociodem_model_brm = baseline_sociodemographic_model_with_missingness_brm(model_formula = m_sociodemographic_daily_w_nopassive, df = daily)
risk_sociodem_model_brm = baseline_sociodemographic_model_with_missingness_brm(model_formula = m_sociodemographic_risk_w_nopassive, df = risk_missing)

# Extract OR
daily_sociodem_or_brm = baseline_sociodemographic_model_odds_ratio(daily_sociodem_model_brm, type = 'Daily Mood Survey', 
                                                              conf_level_corrected = corrected_conf_level,
                                                              bayes=TRUE)

risk_sociodem_or_brm = baseline_sociodemographic_model_odds_ratio(risk_sociodem_model_brm, type = 'Weekly SI Survey', 
                                                              conf_level_corrected = corrected_conf_level,
                                                              bayes=TRUE)

# Combine
combined_sociodem_or_brm = rbind(daily_sociodem_or_brm, risk_sociodem_or_brm)

save(daily_sociodem_model_brm, risk_sociodem_model_brm, combined_sociodem_or_brm, file = 'model_outputs/sociodemographic_predictors_missingness_brm_w_nopassive.rda')
```

# Sociodem plot

```{r}
combined_sociodem_or_brm = combined_sociodem_or_brm %>% dplyr::filter(!grepl('no_passive', term))
sociodem_plot_bayes = make_sociodem_or_plot(sociodem_or_df = combined_sociodem_or_brm, m = m, bayes=TRUE)
```

# Combined plot 
```{r}
fig2_odds_ratio_bayes = cowplot::plot_grid(clinical_or_mlm_bayes, sociodem_plot_bayes, ncol = 1, align = 'v', axis = 'lr',
                   labels = c('A', 'B'), rel_heights = c(1.5, 1))

cowplot::save_plot(fig2_odds_ratio_bayes, filename = '../../figures/supplement/clinical_sociodem_baseline_predictors_with_nopassive_between_missingness_odds_ratio_brm.png',
                   base_height = 10, base_width = 7)
```
