---
title: "Longitudinal analyses of whether changes in clinical self-report measures predicting missingness in the next 30 days"
output: html_document
date: "2022-08-23"
---


# Longitudinal analyses of whether changes in clinical self-report measures predicting missingness in the next 30 days
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Matrix)
library(dbplyr)
library(tidyverse)
library(lme4)
library(emmeans)
library(broom.mixed)
library(lmerTest)
library(brms)
source('model_wrapper_functions.R')
beta_prior = c(prior_string("student_t(3, 0, 10)", class = "b"))
theme_set(theme_bw())
```

# Load daily data


```{r}
load('../../cleaned_data/cleaned_data_for_daily_models.rda')
load('../../cleaned_data/cleaned_baseline_data.rda')
```

```{r}
daily = dplyr::filter(daily, TIMEPNT==6, day_num <=200)
```


# Join in self-report longitudinal data

```{r}
load('../../cleaned_data/cleaned_baseline_data.rda')
```


# Clinical predictors of missingness to examine longitudinally
```{r}
clinical_predictors_longitudinal = c('SHAPS_TOT_r', 'MFQ', 'SCARED', 'SSI19', 'INQ_burdenensomeness', 'INQ_thwartedbelonging')
m = length(clinical_predictors_longitudinal)
conf_level_corrected = 1- (0.05/m)
```


Calculate missingness in the 30-day period following baseline, 1month, and 3month visits
```{r}
selfreport_long_dates = selfreport_long %>%
  pivot_wider(id_cols = ID, values_from = interview_date, names_from = month, names_prefix = 'interview_date_') %>%
  dplyr::filter(complete.cases(.))

daily = left_join(daily, selfreport_long_dates, by = 'ID')


daily_missingness_month_summaries = daily %>%
  group_by(ID) %>%
  mutate(date_period_missing = case_when(
    date >= interview_date_0 & date <= interview_date_0 + 30 & date <= interview_date_1 ~ 0,
    date >= interview_date_1 & date <= interview_date_1 + 30 & date <= interview_date_3 ~ 1,
    date >= interview_date_3 & date <= interview_date_3 + 30 ~ 3,
  )) %>%
  ungroup() %>%
  dplyr::filter(!is.na(date_period_missing)) %>%
  group_by(ID, date_period_missing) %>%
  summarise(daily_missing_pct = mean(missing_daily),
            gps_missing_pct = mean(missing_gps),
            keyboard_missing_pct = mean(missing_keyboard),
            accel_missing_pct = mean(missing_accel)) %>%
  dplyr::rename(.,  month=date_period_missing) %>%
  pivot_longer(contains('pct'), names_to = 'type', values_to = 'missing_pct') %>%
  group_by(ID, type) %>%
  mutate(missing_pct = scale(missing_pct, center = TRUE, scale = FALSE)) %>%
  ungroup() %>%
  group_by(type) %>%
  mutate(missing_pct = scale(missing_pct, center = FALSE, scale = TRUE))


daily_missingness_month_summaries = left_join(daily_missingness_month_summaries, selfreport_long, by = c('ID', 'month'))

# pivot to very long and scale predictors
daily_missingness_month_summaries_long = pivot_longer(daily_missingness_month_summaries, all_of(clinical_predictors_longitudinal),
                                                      names_to = 'clinical_predictor') %>%
  group_by(ID, clinical_predictor, type) %>%
  mutate(value = scale(value, center = TRUE, scale = FALSE)) %>%
  ungroup() %>%
  group_by(clinical_predictor, type, value = scale(value, center = FALSE, scale = TRUE)) %>%
  ungroup()
```


# Run models & save outputs

Within-participant changes in clinical acuity (`value`) used as predictors of changes in % missingness over the next 30 days
```{r}
models_clinical_predict_month_missingness = daily_missingness_month_summaries_long %>%
  group_by(clinical_predictor, type) %>%
  nest() %>%
  mutate(model = purrr::map(data, ~brms::brm(data = ., missing_pct ~ value + month + (value|ID), prior = beta_prior,
                                             cores = 4, chains = 4, iter = 4000, seed = 11291993)),
         coef = purrr::map(model, ~broom::tidy(.)))
  


coef_clinical_predict_month_missingness = models_clinical_predict_month_missingness %>%
  unnest(coef) %>%
  dplyr::select(-data, -model)

save(models_clinical_predict_month_missingness, coef_clinical_predict_month_missingness, file = 'model_outputs/clinical_predict_month_missingness.rda')


load('model_outputs/clinical_predict_month_missingness.rda')
```


# Plot model outputs (coefficients as these are linear regressions)
```{r}
coef_clinical_predict_month_missingness_corrected = models_clinical_predict_month_missingness %>%
  mutate(coef = purrr::map(model, ~broom::tidy(., conf.level = conf_level_corrected))) %>%
  unnest(coef) %>%
  dplyr::select(type, clinical_predictor, term, conf.low_corrected=conf.low, conf.high_corrected = conf.high)


coef_clinical_predict_month_missingness = left_join(coef_clinical_predict_month_missingness, coef_clinical_predict_month_missingness_corrected,
                                                by = c('type', 'clinical_predictor', 'term')) 


coef_clinical_predict_month_missingness = mutate(coef_clinical_predict_month_missingness, 
                                             clinical_predictor = dplyr::recode(clinical_predictor, 
                                                                                'MFQ'='Depression Symptoms (MFQ)',
                                                                                'SHAPS_TOT_r'='Anhedonia Symptoms (SHAPS)',
                                                                                'SCARED'='Anxiety Symptoms (SCARED)', 
                                                                                'SSI19'='Suicidal Ideation Severity (SSI)',
                                                                                'INQ_burdenensomeness'='Percieved Burdensomeness (INQ)', 
                                                                                'INQ_thwartedbelonging'='Thwarted Belonging (INQ)'),
                                             type = dplyr::recode(type,
                                                                  'accel_missing_pct'='Accelerometer',
                                                                  'gps_missing_pct'='GPS',
                                                                  'daily_missing_pct'='Daily Mood Survey',
                                                                  'keyboard_missing_pct'='Keyboard Input')) %>%
  ungroup() %>%
  mutate(sig_star = case_when(
    conf.high*conf.low >= 0 & conf.high_corrected*conf.low_corrected <= 0 ~ '+',
    conf.high*conf.low <= 0 ~ '',
    conf.high_corrected*conf.low_corrected > 0 ~ '#'
  ))

pal2 = c(rgb(0,0,0), rgb(230/255, 159/255,0), rgb(86/255,180/255,233/255), rgb(204/255, 121/255, 167/255), rgb(0, 158/255, 115/255), rgb(0, 114/255, 178/255))

clinical_predict_month_missingness_plot = coef_clinical_predict_month_missingness %>%
  dplyr::filter(term == 'value') %>%
  ggplot(aes(x = clinical_predictor, y = estimate, color = type)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(position = position_dodge(0.3)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0,
                position = position_dodge(0.3), lwd = 1) +
  geom_errorbar(aes(ymin = conf.low_corrected, ymax = conf.high_corrected), width = 0,
                position = position_dodge(0.3)) +
  geom_text(aes(y = conf.high_corrected*1.1, label = sig_star, group = type, color = type),
                position = position_dodge(0.3), show.legend = FALSE) + 
  coord_flip() +
  scale_color_manual(values = pal2) +
  labs(x = 'Within-Person Predictor', y = 'Association with % missing over next 30 days\nStandardized Regression Beta Coefficient', color = 'Missing Data Modality')


ggsave(clinical_predict_month_missingness_plot, file = '../../figures/supplement/clinical_predict_month_missingness.png',
       width = 6, height = 6)

```