---
title: "Autocorelations of Daily Mood, Weekly Suicidal Ideation Frequency, and their Respective Missingness"
output: html_document
date: "2022-08-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Matrix)
library(dbplyr)
library(tidyverse)
library(lubridate)
library(lme4)
library(mice)
library(gghalves)
library(emmeans)
library(naniar)
library(broom.mixed)
library(lmerTest)
library(scales)
library(brms)
options(buildtools.check = function(action) TRUE)
beta_prior = c(prior_string("student_t(3, 0, 10)", class = "b"))
```


# 1. Daily Mood

## Generate daily variables

```{r}
load('../../cleaned_data/cleaned_data_for_daily_models.rda')

daily = daily %>%
  group_by(ID) %>%
  mutate(daily_within = daily- median(daily, na.rm = TRUE),
              daily_lag1 = lag(daily_within, n=1),
              daily_lag2 = lag(daily_within, n=2),
              daily_lag3 = lag(daily_within, n=3),
              daily_lag4 = lag(daily_within, n=4),
              daily_lag5 = lag(daily_within, n=5),
              daily_lag6 = lag(daily_within, n=6),
              daily_lag7 = lag(daily_within, n=7),
              daily_lead1 = lead(daily_within, n=1),
              daily_lead2 = lead(daily_within, n=2),
              daily_lead3 = lead(daily_within, n=3),
              daily_lead4 = lead(daily_within, n=4),
              daily_lead5 = lead(daily_within, n=5),
              daily_lead6 = lead(daily_within, n=6),
              daily_lead7 = lead(daily_within, n=7),
              missing_daily_lag1 = lag(missing_daily, n=1)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(daily_last_week = mean(c(daily_lag1, daily_lag2, daily_lag3, daily_lag4, daily_lag5, daily_lag6, daily_lag7), na.rm=TRUE),
         daily_next_week = mean(c(daily_lead1, daily_lead2, daily_lead3, daily_lead4, daily_lead5, daily_lead6, daily_lead7), na.rm=TRUE)) %>%
  ungroup()


daily = dplyr::filter(daily, day_num <= 200)
daily = dplyr::filter(daily, TIMEPNT==6)
```

##  Does yesterday's or last week's (average) observed daily mood predict today's daily missingness?

```{r}
m_daily_lag1_predict_missing_daily = daily %>%
  brms::brm(data = ., missing_daily ~ daily_lag1 + personal_time_z + weekend + summerbreak + (daily_lag1 |ID),
                                  family = bernoulli(link = 'logit'), chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)

m_daily_lagweek_predict_missing_daily = daily %>%
  brms::brm(data = ., missing_daily ~ daily_last_week + personal_time_z + weekend + summerbreak + (daily_last_week |ID),
                                  family = bernoulli(link = 'logit'), chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)
```

```{r}
# get standard deviation for calculation of odds ratios
daily_sd = sd(daily$daily_within, na.rm = TRUE)

emmeans::emmeans(m_daily_lag1_predict_missing_daily, specs = 'daily_lag1', type = 'response', at = list(daily_lag1 = c(0, daily_sd))) %>%
  pairs(reverse=TRUE) %>%
  confint()


emmeans::emmeans(m_daily_lagweek_predict_missing_daily, specs = 'daily_last_week', type = 'response', 
                 at = list(daily_last_week = c(0, daily_sd))) %>%
  pairs(reverse=TRUE) %>%
  confint()
```

## Autocorrelation of daily mood & daily mood missingness

```{r}
m_daily_missing_autocor = daily %>%
  brms::brm(data = ., missing_daily ~ missing_daily_lag1 + scale(personal_time_z) + weekend + summerbreak + (missing_daily_lag1 |ID),
                                  family = bernoulli(link = 'logit'), chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)

m_daily_autocor = daily %>%
  brms::brm(data = ., scale(daily_within) ~ scale(daily_lag1) + scale(personal_time_z) + weekend + summerbreak + (scale(daily_lag1) |ID),
            chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)

summary(m_daily_missing_autocor)
summary(m_daily_autocor)

broom.mixed::tidy(m_daily_autocor, conf.int = TRUE)

emmeans::emmeans(m_daily_missing_autocor, specs = 'missing_daily_lag1', type = 'response') %>%
  pairs(reverse=TRUE) %>%
  confint()
```

## Does missing daily mood today predict daily mood value tomorrow?

```{r}
m_missing_daily_lag1_predict_daily = daily %>%
  brms::brm(data = ., daily_within ~  missing_daily_lag1 + personal_time_z + weekend + summerbreak + (missing_daily_lag1 |ID),
            chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)


broom.mixed::tidy(m_missing_daily_lag1_predict_daily, conf.int = TRUE)

save(m_daily_autocor, m_daily_missing_autocor,
     m_missing_daily_lag1_predict_daily, 
     m_daily_lag1_predict_missing_daily, 
     m_daily_lagweek_predict_missing_daily, file = 'model_outputs/daily_autocor_models.rda')
```

# 2. Weekly Suicidal Ideation Surveys


## Get data ready for models

```{r}
load('../../cleaned_data/risk.rda')

risk_missing = risk_week_present %>%
  dplyr::filter(week_num <= 28, days ==7) %>%
  group_by(ID) %>%
  mutate(personal_time_z = scale(week_num),
         summerbreak = month %in% c(7, 8),
         site = ifelse(startsWith(ID, '1'), 'CUIMC', 'UPMC'),
         siteCUMC = site == 'CUIMC') %>%
  ungroup()

risk_missing = dplyr::filter(risk_missing, TIMEPNT==6)


risk_weekly_summary = dplyr::filter(risk_weekly, !is.na(riskOne)) %>%
  dplyr::select(ID, week, riskOne) %>%
  ungroup() %>%
  group_by(ID, week) %>%
  summarise(riskOne = max(riskOne))

risk_weekly_summary$riskOne <- recode(risk_weekly_summary$riskOne,"never"=1,"rarely"=2,"sometimes"=3, "often"=4, "allTheTime"=5)

risk_weekly_summary = risk_weekly_summary  %>%
  group_by(ID) %>%
  mutate(si_within = riskOne - mean(riskOne, na.rm = TRUE),
         si_bin = riskOne >= 4) %>%
  ungroup()


risk_missing = left_join(risk_missing, risk_weekly_summary, by = c('ID', 'week'))

risk_missing = risk_missing %>%
  group_by(ID) %>%
  mutate(risk_missing_lag1 = lag(risk_missing, n = 1),
         si_within_lag1 = lag(si_within, n=1),
         si_bin_lag1 = lag(si_bin, n = 1),
         si_between = mean(riskOne, na.rm = TRUE)) %>%
  ungroup()

```

##  Does last week's si predict this week's si survey missingness?

```{r}
m_si_lag1_predict_missing_si = risk_missing %>%
  brms::brm(data = ., risk_missing ~ si_within_lag1 + si_between  + personal_time_z + summerbreak + (si_within_lag1 |ID),
        family = bernoulli(link = 'logit'), chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)

m_si_bin_lag1_predict_missing_si = risk_missing %>%
  brms::brm(data = ., risk_missing ~ si_bin_lag1  + personal_time_z + summerbreak + (si_bin_lag1 |ID),
            family = bernoulli(link = 'logit'), chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)

summary(m_si_lag1_predict_missing_si)
summary(m_si_bin_lag1_predict_missing_si)


emmeans::emmeans(m_si_lag1_predict_missing_si, specs = 'si_within_lag1', type = 'response', at = list(si_within_lag1 = c(0, 1))) %>%
  pairs(reverse=TRUE) %>%
  confint()

```

# Autocorrelation of SI and SI missingness

```{r}
m_si_missing_autocor = risk_missing %>%
  brms::brm(data = ., risk_missing ~ risk_missing_lag1  + personal_time_z + summerbreak + (risk_missing_lag1 |ID),
        family = bernoulli(link = 'logit'), chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)

m_si_autocor = risk_missing %>%
  dplyr::filter(!is.na(si_within), !is.na(si_within_lag1)) %>%
  brms::brm(data = ., si_within ~ si_within_lag1 + personal_time_z + summerbreak + (si_within_lag1 |ID),
            chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)


summary(m_si_autocor)
summary(m_si_missing_autocor)

emmeans::emmeans(m_si_missing_autocor, specs = 'risk_missing_lag1', type = 'response') %>%
  pairs(reverse=TRUE) %>%
  confint()


broom.mixed::tidy(m_si_autocor, conf.int=TRUE)
```


# Does missing SI one week predict higher SI the next?


```{r}
m_missing_si_lag1_predict_si = risk_missing %>%
  brms::brm(data = ., si_within ~  risk_missing_lag1 + personal_time_z + summerbreak + (risk_missing_lag1 |ID),
        chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)

m_missing_si_bin_lag1_predict_si = risk_missing %>%
  brms::brm(data = ., si_bin ~  risk_missing_lag1 + personal_time_z + summerbreak + (risk_missing_lag1 |ID),
        family = bernoulli(link = 'logit'), chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)

options(scipen = 999)
broom.mixed::tidy(m_missing_si_lag1_predict_si, conf.int = TRUE)

summary(m_missing_si_bin_lag1_predict_si)


```


```{r}
save(m_missing_si_bin_lag1_predict_si, m_missing_si_lag1_predict_si,
     m_si_autocor, m_si_missing_autocor,
     m_si_bin_lag1_predict_missing_si, m_si_lag1_predict_missing_si, 
     file = 'model_outputs/si_autocor_models.rda')
```

# Make daily mood plots
```{r}
load('model_outputs/daily_autocor_models.rda')


cond_fx_daily_lag1_predict_missing_daily = conditional_effects(m_daily_lag1_predict_missing_daily)[[1]]  %>%
  ggplot(data = ., aes(x = daily_lag1, y = estimate__)) +
    geom_line(lwd = 2) +
    geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.3) +
    labs(x = 'Daily Mood 1 Day Prior\nRelative to Participant Mean',
         y = 'P(Missing Daily Mood)') +
  theme_bw() +
  xlim(-50, 50)


cond_fx_daily_lagweek_predict_missing_daily = conditional_effects(m_daily_lagweek_predict_missing_daily)[[1]] %>%
  ggplot(data = ., aes(x = daily_last_week, y = estimate__)) +
    geom_line(lwd = 2) +
    geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.3) +
    labs(x = 'Average Daily Mood Over Past Week\nRelative to Participant Mean',
         y = 'P(Missing Daily Mood)') +
  theme_bw() +
  xlim(-50, 50)
  
  
cond_fx_m_daily_missing_autocor = conditional_effects(m_daily_missing_autocor)[[1]] %>%
  dplyr::filter(missing_daily_lag1 %in% c(0, 1)) %>%
  mutate(missing_daily_lag1 = dplyr::recode(missing_daily_lag1, '1'='Missing', '0'='Observed')) %>%
  ggplot(data = ., aes(x = missing_daily_lag1, y = estimate__)) +
    geom_point() +
    geom_errorbar(aes(ymin = lower__, ymax = upper__), width = 0) + 
    theme_bw() +
    labs(x = 'Daily Mood Missingness 1 Day Prior',
         y = 'P(Missing Daily Mood)') 


cond_fx_m_daily_missing_predict_daily = conditional_effects(m_missing_daily_lag1_predict_daily,
                    conditions = data.frame(summerbreak=1, weekend = 0.1))[[1]] %>%
  dplyr::filter(missing_daily_lag1 %in% c(0, 1)) %>%
  mutate(missing_daily_lag1 = dplyr::recode(missing_daily_lag1, '1'='Missing', '0'='Observed')) %>%
  ggplot(data = ., aes(x = missing_daily_lag1, y = estimate__)) +
    geom_point() +
    geom_errorbar(aes(ymin = lower__, ymax = upper__), width = 0) + 
    theme_bw() +
    labs(x = 'Daily Mood Missingness 1 Day Prior',
         y = 'Daily Mood\nRelative to Participant Mean') 


daily_autocor_grid = cowplot::plot_grid(cond_fx_daily_lag1_predict_missing_daily, 
                   cond_fx_daily_lagweek_predict_missing_daily, 
                   cond_fx_m_daily_missing_autocor, cond_fx_m_daily_missing_predict_daily,
                   labels = c('A', 'B', 'C', 'D'))


cowplot::save_plot(daily_autocor_grid, file = '../../figures/supplement/daily_autocor_cond_fx.png', 
                   base_height = 8, base_width = 8)

```

# Make weekly suicidal ideation plots

```{r}
load('model_outputs/si_autocor_models.rda')


si_predict_missing_plt = conditional_effects(m_si_lag1_predict_missing_si)[[1]] %>%
  ggplot(data = ., aes(x = si_within_lag1, y = estimate__)) +
  geom_line(lwd = 2) +
    geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.3) +
    labs(x = 'Suicidal Ideation Frequency 1 Week Prior\nRelative to Participant Mean',
         y = 'P(Missing Weekly SI Survey)') +
    theme_bw() 

missing_predict_si_plt = conditional_effects(m_missing_si_lag1_predict_si)[[1]] %>%
  dplyr::filter(risk_missing_lag1 %in% c(0,1)) %>%
  mutate(risk_missing_lag1 = dplyr::recode(risk_missing_lag1, '1'='Missing', '0'='Observed')) %>%
  ggplot(data = ., aes(x = risk_missing_lag1, y = estimate__)) +
    geom_point() +
    geom_errorbar(aes(ymin = lower__, ymax = upper__), width = 0) + 
    theme_bw() +
    labs(x = 'Weekly SI Survey Missingness 1 Week Prior',
         y = 'Suicide Ideation Frequency\nRelative to Participant Mean') 

si_autocor_plt = conditional_effects(m_si_autocor)[[1]] %>%
  ggplot(data = ., aes(x = si_within_lag1, y = estimate__)) +
  geom_line(lwd = 2) +
    geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.3) +
    labs(x = 'Suicidal Ideation Frequency 1 Week Prior\nRelative to Participant Mean',
         y = 'Suicidal Ideation Frequency\nRelative to Participant Mean') +
    theme_bw() +
  ylim(-2, 2.5)


si_missing_autocor_plt = conditional_effects(m_si_missing_autocor)[[1]] %>%
  dplyr::filter(risk_missing_lag1 %in% c(0,1)) %>%
  mutate(risk_missing_lag1 = dplyr::recode(risk_missing_lag1, '1'='Missing', '0'='Observed')) %>%
  ggplot(data = ., aes(x = risk_missing_lag1, y = estimate__)) +
    geom_point() +
    geom_errorbar(aes(ymin = lower__, ymax = upper__), width = 0) + 
    theme_bw() +
    labs(x = 'Weekly SI Survey Missingness 1 Week Prior',
         y = 'P(Missing Weekly SI Survey)') 


si_autocor_grid = cowplot::plot_grid(si_autocor_plt, si_missing_autocor_plt, 
                   si_predict_missing_plt, missing_predict_si_plt,
                   labels = c('A', 'B', 'C', 'D'))

cowplot::save_plot(si_autocor_grid, file = '../../figures/supplement/risk_autocor_cond_fx.png', 
                   base_height = 8, base_width = 8)


summary(m_si_lag1_predict_missing_si)
```
