---
title: "Analyses of whether missing data precedes or follows changes in suicide ideation frequency"
output: html_document
date: "2022-08-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Matrix)
library(dbplyr)
library(tidyverse)
library(lubridate)
library(lme4)
library(mice)
library(gghalves)
library(emmeans)
library(naniar)
library(broom.mixed)
library(lmerTest)
library(scales)
library(brms)
theme_set(theme_bw())
pal2 = c(rgb(0,0,0), rgb(230/255, 159/255,0), rgb(86/255,180/255,233/255), rgb(204/255, 121/255, 167/255), rgb(0, 158/255, 115/255), rgb(0, 114/255, 178/255))
options(buildtools.check = function(action) TRUE)
beta_prior = c(prior_string("student_t(3, 0, 10)", class = "b"))
```

# Load daily data

```{r}
load('../../cleaned_data/cleaned_data_for_daily_models.rda')
load('../../cleaned_data/cleaned_baseline_data.rda')

daily = left_join(daily, self_report_baseline, by = 'ID')
daily = dplyr::filter(daily, day_num <= 200)
daily = dplyr::filter(daily, TIMEPNT==6)


load('../../cleaned_data/risk.rda')

risk_missing = risk_week_present %>%
  dplyr::filter(week_num <= 28, days ==7) %>%
  group_by(ID) %>%
  mutate(personal_time_z = scale(week_num),
         summerbreak = month %in% c(7, 8),
         site = ifelse(startsWith(ID, '1'), 'CUIMC', 'UPMC'),
         siteCUMC = site == 'CUIMC') %>%
  ungroup() %>%
  left_join(., self_report_baseline, by = 'ID')
```


```{r}
daily = daily %>%
  group_by(ID) %>%
  mutate(missing_daily_lag1 = lag(missing_daily, n= 1),
         missing_gps_lag1 = lag(missing_gps, n=1),
         missing_accel_lag1 = lag(missing_accel, n = 1),
         missing_keyboard_lag1 = lag(missing_keyboard), n = 1,
         daily_within = daily - median(daily, na.rm = TRUE),
         daily_between = median(daily, na.rm = TRUE),
         daily_within_lag1 = lag(daily_within, n = 1)) %>%
  ungroup() %>%
  mutate(daily_within_scaled = scale(daily_within, center = FALSE, scale = TRUE),
         daily_between_scaled = scale(daily_between, center=FALSE, scale = TRUE),
         daily_within_lag1_scaled = scale(daily_within_lag1, center = FALSE, scale = TRUE))
```

# 1: Weekly models -- missingness over a week predict SI?

## Prepare data

```{r}
# Join daily and weekly risk data
daily = mutate(daily, week = floor_date(date, unit = 'week',
                           week_start = getOption("lubridate.week.start", 3)))

risk_weekly$riskOne <- recode(risk_weekly$riskOne,"never"=1,"rarely"=2,"sometimes"=3, "often"=4, "allTheTime"=5)

# Get max SI each week
risk_weekly_summary = risk_weekly %>%
  dplyr::select(ID, week, riskOne) %>%
  ungroup() %>%
  group_by(ID, week) %>%
  summarise(riskOne = max(riskOne, na.rm = TRUE)) 

risk_weekly_summary = risk_weekly_summary %>%
  mutate(risk= ifelse(is.infinite(riskOne), NA_real_, riskOne)) %>%
  group_by(ID) %>%
  mutate(si_within = risk - mean(risk, na.rm = TRUE),
         si_between = mean(risk, na.rm = TRUE),
         si_bin = risk >= 4,
         si_within_lead1 = lead(si_within, n = 1),
         si_bin_lead1 = lead(si_bin, n = 1))

# Summarize daily missingness for each week, and lag 1 week behind to get the 7 days leading up to each SI survey
weekly_si_daily_summary = daily %>%
  dplyr::select(ID, date, daily, daily_lag1, daily_within, daily_between, weekend, week, personal_time_z, summerbreak,
                contains('missing')) %>%
  left_join(., risk_weekly_summary, by = c('ID', 'week')) %>%
  pivot_longer(c('missing_daily', 'missing_gps', 'missing_accel', 'missing_keyboard'),
               names_to = 'name', values_to = 'missing_prop') %>%
  group_by(name, ID, week, si_within) %>%
  summarise(missing_prop = mean(missing_prop)*7, # mean will be # of missing days
            summerbreak=summerbreak[1],
            personal_time_z=personal_time_z[1]) %>%
  ungroup() %>%
  group_by(name, ID) %>%
  arrange(week) %>%
  mutate(missing_prop_lag = lag(missing_prop, n=1)) %>%
  ungroup()
```

## Models

```{r}
models_missingness_predict_si = weekly_si_daily_summary %>% 
  group_by(name) %>%
  nest() %>%
  mutate(model = map(data, ~brms::brm(data = ., si_within ~ missing_prop_lag + summerbreak + personal_time_z + (missing_prop_lag|ID),
                                      chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)),
         coef = map(model, ~broom.mixed::tidy(., conf.int = TRUE))) %>% 
  mutate(name = dplyr::recode(name,
                              'missing_accel'='Accelerometer',
                              'missing_gps'='GPS',
                              'missing_keyboard'='Keyboard Input',
                              'missing_daily'='Daily Mood Survey'))

models_missingness_predict_si_discrete = weekly_si_daily_summary %>% 
  mutate(missing_prop_lag = as.character(round(missing_prop_lag))) %>%
  group_by(name) %>%
  nest() %>%
  mutate(model = map(data, ~brms::brm(data = ., si_within ~ missing_prop_lag + summerbreak + personal_time_z + (missing_prop_lag|ID),
                                      chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)),
         coef = map(model, ~broom.mixed::tidy(., conf.int = TRUE))) %>% 
  mutate(name = dplyr::recode(name,
                              'missing_accel'='Accelerometer',
                              'missing_gps'='GPS',
                              'missing_keyboard'='Keyboard Input',
                              'missing_daily'='Daily Mood Survey'))


brms::prior_summary(models_missingness_predict_si$model[[1]]) 

save(models_missingness_predict_si,
     file = 'model_outputs/missingness_predict_next_week_si_brm.rda')

save(models_missingness_predict_si_discrete,
     file = 'model_outputs/missingness_predict_next_week_si_discrete_brm.rda')
```

```{r}
load('model_outputs/missingness_predict_next_week_si_brm.rda')
load('model_outputs/missingness_predict_next_week_si_discrete_brm.rda')
```

## Extract Coefs

```{r}
m = 4
corrected_conf_level = 1- (0.05/m)


missingness_predict_si_coef = models_missingness_predict_si %>%
  unnest(coef) %>%
  dplyr::select(-data, -model) %>%
  mutate(corrected = 'Uncorrected')

missingness_predict_si_coef_corrected = models_missingness_predict_si %>%
  mutate(coef = map(model, ~broom.mixed::tidy(., conf.int = TRUE, conf.level = corrected_conf_level))) %>% 
  unnest(coef) %>%
  dplyr::select(-data, -model) %>%
  mutate(corrected = 'Corrected')


missingness_predict_si_coef = rbind(missingness_predict_si_coef, missingness_predict_si_coef_corrected)

missingness_predict_si_model_predictions = models_missingness_predict_si %>%
  mutate(preds = purrr::map(model, ~emmeans::emmeans(., specs = 'missing_prop_lag', weights = 'proportional',
                                                     at = list(missing_prop_lag = seq(from = 0, to = 7, by = 1))) %>%
           as.data.frame())) %>%
  unnest(preds) %>%
  dplyr::select(-model, -data)

missingness_predict_si_model_predictions_discrete = models_missingness_predict_si_discrete %>%
  mutate(preds = purrr::map(model, ~emmeans::emmeans(., specs = 'missing_prop_lag', weights = 'proportional',
                                                     at = list(missing_prop_lag = as.character(seq(from = 0, to = 7, by = 1)))) %>%
           as.data.frame())) %>%
  unnest(preds) %>%
  dplyr::select(-model, -data)

```

## Plots

```{r}
missingness_predict_si_coef_plot = missingness_predict_si_coef %>%
  dplyr::filter(term == 'missing_prop_lag', corrected == 'Corrected') %>%
  ggplot(data =., aes(x = name, y = estimate)) +
  geom_hline(yintercept = 0, lty=2) + 
  geom_point(aes(color = name), size = 3) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = name), width = 0) +
  geom_errorbar(data =missingness_predict_si_coef %>%
        dplyr::filter(term == 'missing_prop_lag', corrected == 'Uncorrected'), 
        aes(ymin = conf.low, ymax = conf.high, color = name), width = 0, lwd = 2) +
  coord_flip() + 
  scale_color_manual(values =pal2) +
  theme(legend.position = 'none') +
  labs(x = NULL, y = 'Regression Beta Coefficient', title = 'A) Number of days missing data during 1 week prior as a predictor of suicidal ideation') +
  ylim(-.025, .025) +
  annotate(geom='text', x = 0.67, y = -0.01, label = 'More missing data-->\nless frequent SI next week', size = 4) +
  annotate(geom='text', x = 0.67, y = 0.01, label = 'More missing data-->\nmore frequent SI next week', size = 4)
```


```{r}
missingness_predict_si_coef_for_plot = dplyr::filter(missingness_predict_si_coef, term == 'missing_prop_lag') %>%
  mutate(sig = case_when(conf.low < 0 & conf.high < 0 ~ 1,
                         conf.low > 0 & conf.high > 0 ~ 1,
                         conf.low <= 0 & conf.high >= 0 ~ 0),
         plot_label = paste0('\u03B2', '=', round(estimate, 2), ', 95% CI [', format(round(conf.low, 2), nsmall=2), ', ', format(round(conf.high, 2),nsmall=2), ']'),
         plot_label = ifelse(sig ==1, paste0(plot_label, '\u002A'), plot_label)) %>%
  mutate(name = dplyr::recode(name,
                              'Accelerometer'='Accelerometer',
                              'GPS'='GPS',
                              'Keyboard Input'='Keyboard Input',
                              'Daily Mood Survey'='Daily Mood Survey'))



raw_summary = weekly_si_daily_summary %>%  
  ungroup() %>%
  dplyr::filter(., !is.na(missing_prop_lag),
                round(missing_prop_lag, 6) %in% round(c(0:7), 6)) %>%
  group_by(ID, missing_prop_lag, name) %>%
  summarise(emmean = mean(si_within, na.rm = TRUE),
            n=n()) %>%
  mutate(name = dplyr::recode(name,
                              'missing_accel'='Accelerometer\n% Missing Last Week',
                              'missing_gps'='GPS\n% Missing Last Week',
                              'missing_keyboard'='Keyboard Input\n% Missing Last Week',
                              'missing_daily'='Daily Mood Survey\n% Missing Last Week')) %>%
  mutate(missing_prop_lag = round(missing_prop_lag))

missingness_predict_si_model_predictions = missingness_predict_si_model_predictions %>%
  mutate(name = dplyr::recode(name,
                              'Accelerometer'='Accelerometer',
                              'GPS'='GPS',
                              'Keyboard Input'='Keyboard Input',
                              'Daily Mood Survey'='Daily Mood Survey'))

missingness_predict_si_model_predictions_discrete = missingness_predict_si_model_predictions_discrete %>%
  mutate(name = dplyr::recode(name,
                              'Accelerometer'='Accelerometer',
                              'GPS'='GPS',
                              'Keyboard Input'='Keyboard Input',
                              'Daily Mood Survey'='Daily Mood Survey')) %>%
  mutate(missing_prop_lag = parse_number(as.character(missing_prop_lag)))


missingness_predict_si_plot = ggplot(missingness_predict_si_model_predictions, aes(x = missing_prop_lag, y = emmean)) +
  geom_hline(yintercept = 0, lty = 2) + 
  geom_hline(yintercept = 0.3, alpha = 0) + 
  geom_ribbon(aes(ymin = lower.HPD, ymax = upper.HPD, fill = name), alpha = 0.3) + 
  geom_line(lwd = 2) +
  geom_point(data = missingness_predict_si_model_predictions_discrete, aes(color = name)) +
  geom_errorbar(data = missingness_predict_si_model_predictions_discrete, aes(ymin = lower.HPD, ymax = upper.HPD, color = name), width = 0) + 
  facet_grid(~name) +
  labs(x = 'Days Missing Data During the Week Prior',
       y = 'Suicidal Ideation Frequency\nRelative to Within-Person Average',
       title = 'A: Missing Data as a Within-Person Predictor of Next Week Suicidal Ideation Frequency') +
  scale_fill_manual(values = pal2) +
  scale_color_manual(values = pal2) +
  theme(legend.position = 'none', panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = 0:7)

missingness_predict_si_plot_daily_gps = ggplot(missingness_predict_si_model_predictions %>% dplyr::filter(name %in% c('GPS', 'Daily Mood Survey'))
                                               , aes(x = missing_prop_lag, y = emmean)) +
  geom_hline(yintercept = 0, lty = 2) + 
  geom_hline(yintercept = 0.3, alpha = 0) + 
  geom_ribbon(aes(ymin = lower.HPD, ymax = upper.HPD, fill = name), alpha = 0.3) + 
  geom_line(lwd = 2) +
  geom_point(data = missingness_predict_si_model_predictions_discrete %>% dplyr::filter(name %in% c('GPS', 'Daily Mood Survey')), aes(color = name)) +
  geom_errorbar(data = missingness_predict_si_model_predictions_discrete %>% dplyr::filter(name %in% c('GPS', 'Daily Mood Survey')), aes(ymin = lower.HPD, ymax = upper.HPD, color = name), width = 0) + 
  facet_grid(~name) +
  labs(x = 'Days Missing Data During the Week Prior',
       y = 'Suicidal Ideation Frequency\nRelative to Within-Person Average',
       title = 'A: Missing Data as a Within-Person Predictor of\nNext Week Suicidal Ideation Frequency') +
  scale_fill_manual(values = pal2[2:3]) +
  scale_color_manual(values = pal2[2:3]) +
  theme(legend.position = 'none', panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = 0:7)
```

# 2: Daily Models: does SI predict missingness for the next week?

## Prepare data
```{r}
# Only weeks with observed SI responses
risk_weekly_summary_observed = dplyr::filter(risk_weekly, !is.na(riskOne)) %>%
  dplyr::select(ID, week, riskOne) %>%
  ungroup() %>%
  group_by(ID, week) %>%
  summarise(riskOne = max(riskOne))

risk_weekly_summary_observed$riskOne <- recode(risk_weekly_summary_observed$riskOne,"never"=1,"rarely"=2,"sometimes"=3, "often"=4, "allTheTime"=5)

daily_weekly_si = daily %>%
  dplyr::select(ID, date, daily, daily_lag1, daily_within, daily_between, weekend, week, personal_time_z, summerbreak,
                contains('missing')) %>%
  left_join(., risk_weekly_summary_observed, by = c('ID', 'week'))


daily_weekly_si = daily_weekly_si %>%
  group_by(ID) %>%
  mutate(si_within = riskOne - mean(riskOne, na.rm = TRUE),
         si_between = mean(riskOne, na.rm = TRUE),
         si_bin = riskOne >= 4) %>%
  ungroup()


daily_weekly_si_grouped_weeks = daily_weekly_si %>%
  group_by(ID, week) %>%
  summarize(
         si = riskOne[1],
         si_within = si_within[1],
         si_between = si_between[1],
         si_bin = si_bin[1],
         summerbreak = summerbreak[1],
         personal_time_z = personal_time_z[1],
         prop_missing_daily = mean(missing_daily)*7,
         prop_missing_accel = mean(missing_accel)*7,
         prop_missing_gps = mean(missing_gps)*7,
         prop_missing_keyboard = mean(missing_keyboard)*7)
```

## Models


### Model outcomes daily (with logistic regression)
```{r}
models_si_predict_missingness = daily_weekly_si %>%
  pivot_longer(c(contains('missing'), -contains('lag1'))) %>%
  group_by(name) %>%
  nest() %>%
  mutate(model = map(data, ~brms::brm(data = ., value ~ si_within + si_between + summerbreak + personal_time_z + (si_within|ID),
                                        family = bernoulli(link = 'logit'), chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)))
```

### Model outcomes weekly (with linear regression)
```{r}
models_si_predict_missingness_weekly = daily_weekly_si_grouped_weeks %>%
  pivot_longer(c(contains('prop_missing'))) %>%
  group_by(name) %>%
  nest() %>%
  mutate(model = map(data, ~brms::brm(data = ., value ~ si + summerbreak + personal_time_z + (si|ID),
                                        chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)))

models_si_predict_missingness_weekly_discrete = daily_weekly_si_grouped_weeks %>%
  mutate(si = as.character(si)) %>%
  pivot_longer(c(contains('prop_missing'))) %>%
  group_by(name) %>%
  nest() %>%
  mutate(model = map(data, ~brms::brm(data = ., value ~ si + summerbreak + personal_time_z + (si|ID),
                                        chains = 4, cores = 4, iter = 4000, seed = 11291993, prior = beta_prior)))
```

## Calculate OR


### Daily models
```{r}
or_within_si_predict_missingness = models_si_predict_missingness %>%
  mutate(or = purrr::map(model, ~emmeans::emmeans(., specs = 'si_within', type = 'response',
                                                  at = list('si_within'=c(0,1))) %>%
                           pairs(reverse = TRUE) %>%
                           confint(level = 0.95) %>%
                           data.frame()
    
  )) %>%
  unnest(or) %>%
  dplyr::select(-data, -model) %>%
  mutate('type'='Mean SI Severity')

or_between_si_predict_missingness = models_si_predict_missingness %>%
  mutate(or = purrr::map(model, ~emmeans::emmeans(., specs = 'si_between', type = 'response',
                                                  at = list('si_between'=c(0,1))) %>%
                           pairs(reverse = TRUE) %>%
                           confint(level = 0.99) %>%
                           data.frame()
    
  )) %>%
  unnest(or) %>%
  dplyr::select(-data, -model) %>%
  mutate('type'='Change in SI Severity\nWithin-Person')

models_si_predict_missingness_predictions = models_si_predict_missingness %>%
  mutate(pred_grid = purrr::map(model, ~conditional_effects(., plot = FALSE)$si_within)) %>%
  unnest(pred_grid) %>%
  dplyr::select(-data, -model)
```

### Weekly models
```{r}
coef_si_predict_missingness_weekly = models_si_predict_missingness_weekly %>%
  mutate(coef = map(model, ~broom.mixed::tidy(., conf.int = TRUE))) %>%
  unnest(coef) %>%
  dplyr::select(-data, -model) 

models_si_predict_missingness_predictions_weekly = models_si_predict_missingness_weekly %>%
  mutate(pred_grid = purrr::map(model, ~conditional_effects(., plot = FALSE)$si)) %>%
  unnest(pred_grid) %>%
  dplyr::select(-data, -model)

models_si_predict_missingness_predictions_weekly_discrete = models_si_predict_missingness_weekly_discrete %>%
  mutate(pred_grid = purrr::map(model, ~conditional_effects(., plot = FALSE)$si)) %>%
  unnest(pred_grid) %>%
  dplyr::select(-data, -model) %>%
  mutate(si = parse_number(as.character(si))) %>%
  mutate(name = dplyr::recode(name,
                              'prop_missing_accel'='Accelerometer',
                              'prop_missing_gps'='GPS',
                              'prop_missing_keyboard'='Keyboard Input',
                              'prop_missing_daily'='Daily Mood Survey'),
         lower__ = ifelse(lower__<0, 0, lower__))
```

```{r}
save(models_si_predict_missingness, 
     models_si_predict_missingness_predictions,
     or_within_si_predict_missingness, or_between_si_predict_missingness,
     models_si_predict_missingness_weekly,
     models_si_predict_missingness_weekly_discrete,
     models_si_predict_missingness_predictions_weekly_discrete,
     file = 'model_outputs/si_predict_next_week_missingness_brm.rda')
```

```{r}
load('model_outputs/si_predict_next_week_missingness_brm.rda')
```


## Plots
```{r}
or_within_si_predict_missingness_corrected = models_si_predict_missingness %>%
  mutate(or = purrr::map(model, ~emmeans::emmeans(., specs = 'si_within', type = 'response',
                                                  at = list('si_within'=c(0,1))) %>%
                           pairs(reverse = TRUE) %>%
                           confint(level = m) %>%
                           data.frame()
    
  )) %>%
  unnest(or) %>%
  dplyr::select(-data, -model) %>%
  mutate('type'='Mean SI Severity', 
         corrected = 'Corrected')

or_within_si_predict_missingness = mutate(or_within_si_predict_missingness, corrected = 'Uncorrected')

or_within_si_predict_missingness = rbind(or_within_si_predict_missingness, or_within_si_predict_missingness_corrected)

si_models_or_plot = or_within_si_predict_missingness %>% mutate(name = dplyr::recode(name,
                              'missing_accel'='Accelerometer',
                              'missing_gps'='GPS',
                              'missing_keyboard'='Keyboard Input',
                              'missing_daily'='Daily Mood Survey')) %>%
  dplyr::filter(corrected == 'Corrected') %>%
  ggplot(data = ., aes(x = name, y = odds.ratio)) +
  geom_hline(yintercept = 1, lty=2) + 
  geom_point(aes(color = name), size = 3) +
  geom_errorbar(data = or_within_si_predict_missingness %>% mutate(name = dplyr::recode(name,
                              'missing_accel'='Accelerometer',
                              'missing_gps'='GPS',
                              'missing_keyboard'='Keyboard Input',
                              'missing_daily'='Daily Mood Survey')) %>%
                            dplyr::filter(corrected == 'Uncorrected'), 
                aes(ymin = lower.HPD, ymax = upper.HPD, color = name), width = 0, lwd = 2) +
  geom_errorbar(aes(ymin = lower.HPD, ymax = upper.HPD, color = name), width = 0) +
  coord_flip() + 
  scale_y_log10() +
  scale_color_manual(values =pal2) +
  theme(legend.position = 'none') +
  labs(x = NULL, y = 'Adjusted Odds Ratio', title = 'B) Suicidal ideation as a predictor of missing data probability over the next week') +
  annotate(geom='text', x = 0.67, y = 0.8, label = 'More frequent SI-->\nless missing data next week', size = 4) +
  annotate(geom='text', x = 0.67, y = 1.3, label = 'More frequent SI-->\nmore missing data next week', size = 4) 

```

```{r}
alt_fig5 = cowplot::plot_grid(missingness_predict_si_coef_plot, si_models_or_plot, nrow = 2)
cowplot::save_plot(alt_fig5, filename = '../../figures/fig8.2_si_missingness_stats.png', base_width = 9, base_height = 7)
```

## Marginal Predictions Plots for SI predicting missingness

```{r}
si_models_curves_plot = models_si_predict_missingness_predictions %>%
  mutate(name = dplyr::recode(name,
                              'missing_accel'='Accelerometer',
                              'missing_gps'='GPS',
                              'missing_keyboard'='Keyboard Input',
                              'missing_daily'='Daily Mood Survey')) %>%
  ggplot(data = ., aes(x = si, y = estimate__)) +
  geom_line() + 
  geom_ribbon(aes(ymin = lower__, ymax = upper__, fill= name), alpha = 0.3) +
  facet_grid(~name) +
  labs(y = 'P(Missing)\nDuring the next week', x = 'Suicidal Ideation Frequency\nRelative to Within-Person Average') +
  scale_fill_manual(values = pal2) +
  theme(legend.position = 'none')

coef_within_si_predict_missingness_weekly_for_plot = dplyr::filter(coef_si_predict_missingness_weekly,
                                                                   term == 'si') %>%
  mutate(sig = case_when(conf.low < 0 & conf.high < 0 ~ 1,
                         conf.low > 0 & conf.high > 0 ~ 1,
                         conf.low <= 0 & conf.high >= 0 ~ 0),
        name = dplyr::recode(name,
                              'prop_missing_accel'='Accelerometer',
                              'prop_missing_gps'='GPS',
                              'prop_missing_keyboard'='Keyboard Input',
                              'prop_missing_daily'='Daily Mood Survey'),
         plot_label = paste0('\u03B2', '=', round(estimate, 2), ', 95% CI [', format(round(conf.low, 2), nsmall=2), ', ', format(round(conf.high, 2),nsmall=2), ']'),
         plot_label = ifelse(sig ==1, paste0(plot_label, '\u002A'), plot_label))


daily_weekly_si_grouped_weeks_bins = daily_weekly_si_grouped_weeks %>%
  dplyr::filter(is.numeric(si), !is.na(si)) %>%
  pivot_longer(c(contains('prop_missing'))) %>%
  group_by(ID, name, si) %>%
  summarise(`estimate__`=mean(value)) %>%
  mutate(name = dplyr::recode(name,
                              'prop_missing_accel'='Accelerometer\n% Missing Next Week',
                              'prop_missing_gps'='GPS\n% Missing Next Week',
                              'prop_missing_keyboard'='Keyboard Input\n% Missing Next Week',
                              'prop_missing_daily'='Daily Mood Survey\n% Missing Next Week')) 

si_models_curves_weekly_plot = models_si_predict_missingness_predictions_weekly %>%
  mutate(name = dplyr::recode(name,
                              'prop_missing_accel'='Accelerometer',
                              'prop_missing_gps'='GPS',
                              'prop_missing_keyboard'='Keyboard Input',
                              'prop_missing_daily'='Daily Mood Survey')) %>%
  ggplot(data = ., aes(x = si, y = estimate__)) +
  geom_line(lwd = 2) + 
  geom_point(data = models_si_predict_missingness_predictions_weekly_discrete, aes(color = name)) +
  geom_errorbar(data = models_si_predict_missingness_predictions_weekly_discrete, aes(ymin = lower__, ymax = upper__, color = name), 
                width = 0) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__, fill= name), alpha = 0.3) +
  facet_grid(~name) +
  labs(y = 'Days Missing Data\nDuring the next week', x = 'Suicidal Ideation Frequency\n1=Never, 2=Rarely, 3=Sometimes, 4=Frequently, 4=All The Time',
       title = 'B: Suicidal Ideation Frequency as a Within-Person Predictor of Missing Data Over the Next Week') +
  scale_fill_manual(values = pal2) +
  scale_color_manual(values = pal2) +
  theme(legend.position = 'none') +
  ylim(0,7) 

si_models_curves_weekly_plot_gps_daily = models_si_predict_missingness_predictions_weekly %>%
  mutate(name = dplyr::recode(name,
                              'prop_missing_accel'='Accelerometer',
                              'prop_missing_gps'='GPS',
                              'prop_missing_keyboard'='Keyboard Input',
                              'prop_missing_daily'='Daily Mood Survey')) %>%
  dplyr::filter(name %in% c('GPS', 'Daily Mood Survey')) %>%
  ggplot(data = ., aes(x = si, y = estimate__)) +
  geom_line(lwd = 2) + 
  geom_point(data = models_si_predict_missingness_predictions_weekly_discrete %>% dplyr::filter(name %in% c('GPS', 'Daily Mood Survey')), 
             aes(color = name)) +
  geom_errorbar(data = models_si_predict_missingness_predictions_weekly_discrete %>% dplyr::filter(name %in% c('GPS', 'Daily Mood Survey')), 
                aes(ymin = lower__, ymax = upper__, color = name), 
                width = 0) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__, fill= name), alpha = 0.3) +
  facet_grid(~name) +
  labs(y = 'Days Missing Data\nDuring the next week', x = 'Suicidal Ideation Frequency\n1=Never, 2=Rarely, 3=Sometimes, 4=Frequently, 4=All The Time',
       title = 'B: Suicidal Ideation Frequency as a Within-Person Predictor of\nMissing Data Over the Next Week') +
  scale_fill_manual(values = pal2[2:3]) +
  scale_color_manual(values = pal2[2:3]) +
  theme(legend.position = 'none') +
  ylim(0,7) 
  
```

# 3: Assemble grid for Marginal Prediction Plots

```{r}
si_missingness_grid = cowplot::plot_grid(missingness_predict_si_plot, si_models_curves_weekly_plot,
                                         nrow = 2,
                                         align = 'v', axis = 'lr')

si_missingness_daily_gps= cowplot::plot_grid(missingness_predict_si_plot_daily_gps, si_models_curves_weekly_plot_gps_daily,
                                         nrow = 2,
                                         align = 'v', axis = 'lr')

cowplot::save_plot(si_missingness_grid, file = '../../figures/fig8.1_si_missingness.png',
                   base_height = 6, base_width = 9.5)

cowplot::save_plot(si_missingness_daily_gps, file = '../../figures/fig8.1_si_missingness_daily_gps.png',
                   base_height = 6, base_width = 6)
```

